Using Nature Inspired Algorithms for Feature Selection in Transaction Fraud Detection

### 2020-05-31 paper/main.tex
Fix figure
Fix details in paper

\begin{figure}
    \centering
    \includegraphics[width=11cm]{figures/nia_train_score_by_algorithm_10}
    \caption{Scores of the nature-inspired in 5 runs algorithms for population size of 10.}
    \label{fig:nia_train_score_by_algorithm_1}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=11cm]{figures/nia_train_score_by_algorithm_10}
    \caption{Scores of the nature-inspired algorithms in 5 runs for population size of 50.}
    \label{fig:nia_train_score_by_algorithm_2}
\end{figure}

\def\arraystretch{1.5}
\begin{table}
	\begin{center}
		\caption{Highest train scores (ROC AUC) of nature inspired algorithms by population size. We may notice that Grey Wolf Algorithm (GWO) outperformed all of the other algorithms.} \label{tab:nia_comparison}
	\end{center}
	\begin{center}
		\begin{tabular}{|l|r|r|r|r|r|}
			\hline
			\textbf{Population size \textbackslash Score} & \multicolumn{1}{r|}{\textbf{FA}} & \multicolumn{1}{r|}{\textbf{CS}} & \multicolumn{1}{r|}{\textbf{BA}} & \multicolumn{1}{r|}{\textbf{FPA}} & \multicolumn{1}{r|}{\textbf{GWO}} \\ \hline
			\textbf{10}                                             & 0.753                           & \textbf{0.752}                           & 0.759                           & 0.754                            & 0.776                             \\
			\textbf{20}                                             & 0.757                           & 0.746                           & 0.755                           & 0.750                            & 0.771                             \\
			\textbf{50}                                             & \textbf{0.761}                           & 0.751                           & \textbf{0.761}                           & \textbf{0.756}                            & \textbf{0.782}                             \\ \hline
		\end{tabular}
	\end{center}
\end{table}

All of the nature-inspired algorithms perform roughly the same, except the Grey Wolf Optimizer which outperformed the others (Figure \ref{fig:nia_train_score_by_algorithm}). These differences in results between GWO and other algorithms are significant (there is a sigificant difference in means, t-test; $p-value=0.012$). Looking for the explanation, we found out that only Grey Wolf Algorithm and Bat Algorithm converged during the optimization run. Figure \ref{fig:nia_scores_by_run_1}. \& \ref{fig:nia_scores_by_run_2}. shows the optimization progress of the Firefly Algorithm and Grey Wolf Optimizer, Firefly Algorithm did not converge. If we fine-tuned the parameters of other algorithms, they might converge as well. The fact that GWO does not have any parameters (except the population size) might be an advantage for it in our experiments.

@@

\begin{figure}[h!]
	\begin{center}
	    \includegraphics[width=10cm]{figures/nia_selected_features_by_algorithm.png}
    \end{center}
	\caption{Number of selected features by algorithm in 5 runs - Grey Wolf Algorithm selected by far the least number of features.}
	\label{fig:nia_selected_features_by_algorithm}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=11cm]{figures/nia_train_score_by_algorithm_10}
    \caption{Scores of the nature-inspired algorithms in 5 runs - population size of 10.}
    \label{fig:nia_train_score_by_algorithm_1}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=11cm]{figures/nia_train_score_by_algorithm_50}
    \caption{Scores of the nature-inspired algorithms in 5 runs - population size of 50.}
    \label{fig:nia_train_score_by_algorithm_2}
\end{figure}

\def\arraystretch{1.5}
\begin{table}
	\vspace*{0.5cm}
	\begin{center}
		\caption{Highest train scores (ROC AUC) of nature inspired algorithms by population size. We may notice that Grey Wolf Algorithm (GWO) outperformed all of the other algorithms.} \label{tab:nia_comparison}
	\end{center}
	\begin{center}
		\begin{tabular}{|l|r|r|r|r|r|}
			\hline
			\textbf{Population size \textbackslash Score} & \multicolumn{1}{r|}{\textbf{FA}} & \multicolumn{1}{r|}{\textbf{CS}} & \multicolumn{1}{r|}{\textbf{BA}} & \multicolumn{1}{r|}{\textbf{FPA}} & \multicolumn{1}{r|}{\textbf{GWO}} \\ \hline
			\textbf{10}                                             & 0.753                           & \textbf{0.752}                           & 0.759                           & 0.754                            & 0.776                             \\
			\textbf{20}                                             & 0.757                           & 0.746                           & 0.755                           & 0.750                            & 0.771                             \\
			\textbf{50}                                             & \textbf{0.761}                           & 0.751                           & \textbf{0.761}                           & \textbf{0.756}                            & \textbf{0.782}                             \\ \hline
		\end{tabular}
	\end{center}
\end{table}

All of the nature-inspired algorithms perform roughly the same, except the Grey Wolf Optimizer which outperformed the others (Figure \ref{fig:nia_train_score_by_algorithm_1} \& \ref{fig:nia_train_score_by_algorithm_2}). These differences in results between GWO and other algorithms are significant (there is a sigificant difference in means, t-test; $p-value=0.012$). Looking for the explanation, we found out that only Grey Wolf Algorithm and Bat Algorithm converged during the optimization run. Figure \ref{fig:nia_scores_by_run_1}. \& \ref{fig:nia_scores_by_run_2}. shows the optimization progress of the Firefly Algorithm and Grey Wolf Optimizer, Firefly Algorithm did not converge. If we fine-tuned the parameters of other algorithms, they might converge as well. The fact that GWO does not have any parameters (except the population size) might be an advantage for it in our experiments.

@@

\begin{figure}[h!]
	\vspace*{1cm}
	\begin{center}
	    \includegraphics[width=10cm]{figures/nia_selected_features_by_algorithm.png}
    \end{center}
	\caption{Number of selected features by algorithm in 5 runs - Grey Wolf Algorithm selected by far the least number of features.}
	\label{fig:nia_selected_features_by_algorithm}
\end{figure}
